Inferring Lensing Mass in the Universe \\ from Photometric Catalog Data

### 2012-10-08 doc/references.tex
refs added to intro, figs tidied away

\bibitem[\protect\citeauthoryear{Auger et al.}{2009}]{Auger++2009} 
Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
P.~J., Bundy K., Moustakas L.~A., 2009, ApJ, 705, 1099

\bibitem[\protect\citeauthoryear{Auger et al.}{2010}]{Auger++2010} 
Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
P.~J., Moustakas L.~A., Burles S., 2010, ApJ, 724, 511

@@

\bibitem[\protect\citeauthoryear{Behroozi, Conroy, 
\& Wechsler}{2010}]{Behroozi++2009} Behroozi P.~S., Conroy C., Wechsler R.~H., 2010, ApJ, 717, 379

@@

\bibitem[\protect\citeauthoryear{Collett et 
al.}{2012}]{Collett++2012a} Collett T.~E., Auger M.~W., Belokurov V., 
Marshall P.~J., Hall A.~C., 2012, MNRAS, 424, 2864

@@

\bibitem[\protect\citeauthoryear{Falco, Gorenstein, 
\& Shapiro}{1985}]{Falco++1985} Falco E.~E., Gorenstein M.~V., Shapiro I.~I., 1985, ApJ, 289, L1

\bibitem[\protect\citeauthoryear{Fassnacht, Koopmans, 
\& Wong}{2011}]{Fassnacht++2011} Fassnacht C.~D., Koopmans L.~V.~E., Wong K.~C., 2011, MNRAS, 410, 2167

\bibitem[\protect\citeauthoryear{Gavazzi et 
al.}{2008}]{Gavazzi++2008} Gavazzi R., Treu T., Koopmans L.~V.~E., 
Bolton A.~S., Moustakas L.~A., Burles S., Marshall P.~J., 2008, ApJ, 677, 
1046

\bibitem[\protect\citeauthoryear{Hilbert et 
al.}{2009}]{2009A&A...499...31H} Hilbert S., Hartlap J., White S.~D.~M., Schneider P., 2009, A\&A, 499, 31

@@

@@

\bibitem[\protect\citeauthoryear{Nandra, Lasenby, 
\& Hobson}{2012}]{Nandra++2012} Nandra R., Lasenby A.~N., Hobson M.~P., 2012, MNRAS, 422, 2945

@@

@@

\bibitem[\protect\citeauthoryear{Springel et 
al.}{2005}]{Springel++2005} Springel V., et al., 2005, Natur, 435, 629

\bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012b} Suyu 
S.~H., 2012, arXiv, arXiv:1202.0287

\bibitem[\protect\citeauthoryear{Suyu et al.}{2012}]{Suyu++2012a} 
Suyu S.~H., et al., 2012, arXiv, arXiv:1208.6010

\bibitem[\protect\citeauthoryear{Suyu et al.}{2010}]{Suyu++2010} 
Suyu S.~H., Marshall P.~J., Auger M.~W., Hilbert S., Blandford R.~D., 
Koopmans L.~V.~E., Fassnacht C.~D., Treu T., 2010, ApJ, 711, 201

@@

\bibitem[\protect\citeauthoryear{Wong et al.}{2011}]{Wong++2011} 
Wong K.~C., Keeton C.~R., Williams K.~A., Momcheva I.~G., Zabludoff A.~I., 
2011, ApJ, 726, 84

>>>>

\bibitem[{{Auger} {et~al.}(2007){Auger}, {Fassnacht}, {Abrahamse}, {Lubin}, \&
  {Squires}}]{AugerEtal2007}
{Auger}, M.~W., {Fassnacht}, C.~D., {Abrahamse}, A.~L., {Lubin}, L.~M., \&
  {Squires}, G.~K. 2007, \aj, 134, 668

\bibitem[\protect\citeauthoryear{Auger et al.}{2009}]{AugerEtal2009} 
Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
P.~J., Bundy K., Moustakas L.~A., 2009, ApJ, 705, 1099

\bibitem[\protect\citeauthoryear{Auger et al.}{2010}]{AugerEtal2010} 
Auger M.~W., Treu T., Bolton A.~S., Gavazzi R., Koopmans L.~V.~E., Marshall 
P.~J., Moustakas L.~A., Burles S., 2010, ApJ, 724, 511

@@

\bibitem[\protect\citeauthoryear{Behroozi, Conroy, 
\& Wechsler}{2010}]{BehrooziEtal2009} Behroozi P.~S., Conroy C., Wechsler R.~H., 2010, ApJ, 717, 379

@@

\bibitem[{{Brada{\v c}} {et~al.}(2009){Brada{\v c}}, {Treu}, {Applegate},
  {Gonzalez}, {Clowe}, {Forman}, {Jones}, {Marshall}, {Schneider}, \&
  {Zaritsky}}]{BradacEtal2009}
{Brada{\v c}}, M., {et~al.} 2009, \apj, 706, 1201

\bibitem[\protect\citeauthoryear{Collett et 
al.}{2012}]{CollettEtal2012a} Collett T.~E., Auger M.~W., Belokurov V., 
Marshall P.~J., Hall A.~C., 2012, MNRAS, 424, 2864

\bibitem[Dalal(2005)]{Dalal2005} Dalal, N.\ 2005, 25 Years After 
the Discovery: Some Current Topics on Lensed QSOs,

\bibitem[{{Dalal} {et~al.}(2005){Dalal}, {Hennawi}, \& {Bode}}]{DalalEtal2005}
{Dalal}, N., {Hennawi}, J.~F., \& {Bode}, P. 2005, \apj, 622, 99

@@

\bibitem[\protect\citeauthoryear{Falco, Gorenstein, 
\& Shapiro}{1985}]{FalcoEtal1985} Falco E.~E., Gorenstein M.~V., Shapiro I.~I., 1985, ApJ, 289, L1

\bibitem[{{Fassnacht} \& {Lubin}(2002)}]{Fassnacht+Lubin2002}
{Fassnacht}, C.~D., \& {Lubin}, L.~M. 2002, \aj, 123, 627

\bibitem[\protect\citeauthoryear{Fassnacht, Koopmans, 
\& Wong}{2011}]{FassnachtEtal2011} Fassnacht C.~D., Koopmans L.~V.~E., Wong K.~C., 2011, MNRAS, 410, 2167

\bibitem[\protect\citeauthoryear{Gavazzi et 
al.}{2008}]{GavazziEtal2008} Gavazzi R., Treu T., Koopmans L.~V.~E., 
Bolton A.~S., Moustakas L.~A., Burles S., Marshall P.~J., 2008, ApJ, 677, 
1046

\bibitem[{{Hilbert} {et~al.}(2007){Hilbert}, {White}, {Hartlap}, \&
  {Schneider}}]{HilbertEtal2007}
{Hilbert}, S., {White}, S.~D.~M., {Hartlap}, J., \& {Schneider}, P. 2007,
  \mnras, 382, 121

\bibitem[\protect\citeauthoryear{Hilbert et 
al.}{2009}]{HilbertEtal2009} Hilbert S., Hartlap J., White S.~D.~M., Schneider P., 2009, A\&A, 499, 31

\bibitem[Holder 
\& Schechter(2003)]{Holder+Schechter2003} Holder, G.~P., \& Schechter, P.~L.\ 2003, \apj, 589, 688

@@

\bibitem[{{Keeton} \& {Zabludoff}(2004)}]{Keeton+Zabludoff2004}
{Keeton}, C.~R., \& {Zabludoff}, A.~I. 2004, \apj, 612, 660

@@

\bibitem[{{Momcheva} {et~al.}(2006){Momcheva}, {Williams}, {Keeton}, \&
  {Zabludoff}}]{MomchevaEtal2006}
{Momcheva}, I., {Williams}, K., {Keeton}, C., \& {Zabludoff}, A. 2006, \apj,
  641, 169

\bibitem[\protect\citeauthoryear{Nandra, Lasenby, 
\& Hobson}{2012}]{NandraEtal2012} Nandra R., Lasenby A.~N., Hobson M.~P., 2012, MNRAS, 422, 2945

@@

\bibitem[{{Oguri} \& {Takahashi}(2006)}]{Oguri+Takahashi2006}
{Oguri}, M., \& {Takahashi}, K. 2006, \prd, 73, 123002

@@

\bibitem[\protect\citeauthoryear{Springel et 
al.}{2005}]{SpringelEtal2005} Springel V., et al., 2005, Natur, 435, 629

% \bibitem[\protect\citeauthoryear{Suyu}{2012}]{Suyu2012b} Suyu 
% S.~H., 2012, arXiv, arXiv:1202.0287

\bibitem[\protect\citeauthoryear{Suyu et al.}{2012}]{SuyuEtal2012} 
Suyu S.~H., et al., 2012, arXiv, arXiv:1208.6010

\bibitem[\protect\citeauthoryear{Suyu et al.}{2010}]{SuyuEtal2010} 
Suyu S.~H., Marshall P.~J., Auger M.~W., Hilbert S., Blandford R.~D., 
Koopmans L.~V.~E., Fassnacht C.~D., Treu T., 2010, ApJ, 711, 201

@@

\bibitem[{{Wang} \& {Dai}(2011)}]{Wang+Dai2011}
{Wang}, F.~Y., \& {Dai}, Z.~G. 2011, \aap, 536, A96

\bibitem[{{Williams} {et~al.}(2006){Williams}, {Momcheva}, {Keeton},
  {Zabludoff}, \& {Leh{\'a}r}}]{WilliamsEtal2006}
{Williams}, K.~A., {Momcheva}, I., {Keeton}, C.~R., {Zabludoff}, A.~I., \&
  {Leh{\'a}r}, J. 2006, \apj, 646, 85

\bibitem[\protect\citeauthoryear{Wong et al.}{2011}]{WongEtal2011} 
Wong K.~C., Keeton C.~R., Williams K.~A., Momcheva I.~G., Zabludoff A.~I., 
2011, ApJ, 726, 84

\bibitem[{{Wong} {et~al.}(2012){Wong}, {Ammons}, {Keeton}, \&
  {Zabludoff}}]{WongEtal2012}
{Wong}, K.~C., {Ammons}, S.~M., {Keeton}, C.~R., \& {Zabludoff}, A.~I. 2012,
  \apj, 752, 104
